### 2022-09-30 inst/Examples/Paper_results/Paper_results_1.Rmd
Minor changes in linrampfitter.R
if NA is inserted into opt.params, then replace with default value

```{r events_all, evals=TRUE}
agesimmatrix_dust = matrix(NA,29,nsims)
agesimmatrix_d18O = matrix(NA,29,nsims)
depthlist_dust = c()
depthlist_d18O = c()
do.plot.rampfit = FALSE
do.plot.agehist = FALSE
depthstats = as.data.frame(matrix(NA,7,29))
colnames(depthstats) = c("true", "mean", "CIL","CIU","dustmean","dustCIL","dustCIU")
agestats = as.data.frame(matrix(NA,7,29))
colnames(agestats) = c("true", "mean", "CIL","CIU","dustmean","dustCIL","dustCIU")
# below is some fiddling with optimization parameters to improve the linear ramp fit for 
# some of the more challenging fits
steplengths = rep(0.005,29) 
steplengths[c(5,10)]=0.0001 #sometimes changing the steplength in the INLA optimization procedure can improve convergence (default is 0.005)
#compute.dust = rep(TRUE,29); compute.dust[c(8,27)]=FALSE #
#dtparams1 = rep(1,29); dtparams2 = rep(0.2,29) #prior-parameters for transition length
#t0params1 = rep(1,29); t0params2 = rep(0.2,29) #prior-parameters for transition onset
#dtparams1[10] = 20; dtparams2[10] = 0.1 #
#t0params1[10] = 120; t0params2[10] = 20
for(eventnumber in 1:29){
  if(eventnumber == 10){ #one of the transitions struggled to find good initial value 
    opt.params = c(40,NA,NA,NA) #for onset depth
    priorparams=NULL
  }else{
    opt.params = NULL
    priorparams=NULL
  }

@@

  temp_d18O = linrampfitter(results,control.linramp_d18O)
  if(do.plot.rampfit){
    {
      plot(depth[interval_d18O],proxy[interval_d18O],type="l",col="gray",
          xlim=rev(range(depth[interval_d18O])), xlab="Depth (m)",ylab=expression(paste(delta^18,"O (permil)")),
          main=paste0(eventnumber," (d18O): ", event_intervals[eventnumber,2]))
      lines(temp_d18O$linramp$data$x,temp_d18O$linramp$linrampfit$mean)
      lines(temp_d18O$linramp$data$x,temp_d18O$linramp$linrampfit$q0.025,col="red")
      lines(temp_d18O$linramp$data$x,temp_d18O$linramp$linrampfit$q0.975,col="red")
      abline(v=rasmussen_depths[eventnumber],lty=3)

      ybottom = min(temp_d18O$linramp$data$y)
      ytop = min(temp_d18O$linramp$linrampfit$q0.025)
      margt0=temp_d18O$linramp$param$t0$marg.t0
      normt0.y = margt0[,2]/diff(range(margt0[,2]))*(ytop-ybottom)-min(margt0[,2])+ybottom
      lines(x=margt0[,1],y=normt0.y,col="blue",lwd=2)
      ybottom = min(temp_d18O$linramp$data$y)
      ytop = min(temp_d18O$linramp$linrampfit$q0.025)
      margt1 = temp_d18O$linramp$param$t1$marginal
      normt1.y = margt1[,2]/diff(range(margt1[,2]))*(ytop-ybottom)-min(margt1[,2])+ybottom
      lines(x=margt1[,1],y=normt1.y,col="blue",lwd=2,lty=3)
    }
  }
  temp_dust = linrampfitter(results_dust,control.linramp_dust)
  if(do.plot.rampfit){
    {
      plot(temp_dust$linramp$data$x,temp_dust$linramp$data$y,type="l",col="gray",xlim=rev(range(depth[interval_dust])), xlab="Depth (m)",ylab=expression(paste("log(Ca)","")),
          main=paste0(eventnumber," (logdust): ", event_intervals[eventnumber,2]))
      # plot(depth[interval_d18O],logdust[interval_d18O],type="l",col="gray",xlim=rev(range(depth[interval_dust])), xlab="Depth (m)",ylab=expression(paste("log(Ca)","")),
      #     main=paste0(eventnumber," (logdust): ", event_intervals[eventnumber,2]))
      lines(temp_dust$linramp$data$x,temp_dust$linramp$linrampfit$mean)
      lines(temp_dust$linramp$data$x,temp_dust$linramp$linrampfit$q0.025,col="red")
      lines(temp_dust$linramp$data$x,temp_dust$linramp$linrampfit$q0.975,col="red")
      abline(v=rasmussen_depths[eventnumber],lty=3)

      ybottom = min(temp_dust$linramp$data$y)
      ytop = min(temp_dust$linramp$linrampfit$q0.025)
      margt0=temp_dust$linramp$param$t0$marg.t0
      normt0.y = margt0[,2]/diff(range(margt0[,2]))*(ytop-ybottom)-min(margt0[,2])+ybottom
      lines(x=margt0[,1],y=normt0.y,col="blue",lwd=2)
      ybottom = min(temp_dust$linramp$data$y)
      ytop = min(temp_dust$linramp$linrampfit$q0.025)
      margt1 = temp_dust$linramp$param$t1$marginal
      normt1.y = margt1[,2]/diff(range(margt1[,2]))*(ytop-ybottom)-min(margt1[,2])+ybottom
      lines(x=margt1[,1],y=normt1.y,col="blue",lwd=2,lty=3)
    }
  }

>>>>

```{r events_all, evals=TRUE}
agesimmatrix_dust = matrix(NA,29,nsims)
agesimmatrix_d18O = matrix(NA,29,nsims)
depthlist_dust = c()
depthlist_d18O = c()
do.plot.rampfit = TRUE
do.plot.agehist = FALSE
depthstats = as.data.frame(matrix(NA,7,29))
colnames(depthstats) = c("true", "mean", "CIL","CIU","dustmean","dustCIL","dustCIU")
agestats = as.data.frame(matrix(NA,7,29))
colnames(agestats) = c("true", "mean", "CIL","CIU","dustmean","dustCIL","dustCIU")
# below is some fiddling with optimization parameters to improve the linear ramp fit for 
# some of the more challenging fits
steplengths = rep(0.005,29) 
steplengths[c(5,10)]=0.0001 #sometimes changing the steplength in the INLA optimization procedure can improve convergence (default is 0.005)
#compute.dust = rep(TRUE,29); compute.dust[c(8,27)]=FALSE #
#dtparams1 = rep(1,29); dtparams2 = rep(0.2,29) #prior-parameters for transition length
#t0params1 = rep(1,29); t0params2 = rep(0.2,29) #prior-parameters for transition onset
#dtparams1[10] = 20; dtparams2[10] = 0.1 #
#t0params1[10] = 120; t0params2[10] = 20
for(eventnumber in 1:29){
  if(eventnumber == 10){ #one of the transitions struggled to find good initial value 
    opt.params = c(40,NA,NA,NA) #for onset depth
    priorparams=NULL
  }else{
    opt.params = NULL
    priorparams=NULL
  }

@@

  temp_d18O = linrampfitter(results,control.linramp_d18O)
  if(do.plot.rampfit){
    {
      ybottom = min(temp_d18O$linramp$data$y)
      ytop = min(temp_d18O$linramp$linrampfit$q0.025)
      epsilon = (ytop-ybottom)*0.3

      margt0=temp_d18O$linramp$param$t0$marg.t0
      normt0.y = (margt0[,2]-min(margt0[,2]))/diff(range(margt0[,2]))*(ytop-ybottom)+ybottom-epsilon
      margt1 = temp_d18O$linramp$param$t1$marginal
      normt1.y = margt1[,2]/diff(range(margt1[,2]))*(ytop-ybottom)-min(margt1[,2])+ybottom-epsilon

      yrange = range(temp_d18O$linramp$data$y,temp_d18O$linramp$linrampfit$q0.025,
                     temp_d18O$linramp$linrampfit$q0.975,
                     normt0.y,normt1.y)

      plot(depth[interval_d18O],proxy[interval_d18O],type="l",col="gray",
          xlim=rev(range(depth[interval_d18O])), xlab="Depth (m)",ylab=expression(paste(delta^18,"O (permil)")),
          main=paste0(eventnumber," (d18O): ", event_intervals[eventnumber,2]),
          ylim=yrange)
      lines(temp_d18O$linramp$data$x,temp_d18O$linramp$linrampfit$mean)
      lines(temp_d18O$linramp$data$x,temp_d18O$linramp$linrampfit$q0.025,col="red")
      lines(temp_d18O$linramp$data$x,temp_d18O$linramp$linrampfit$q0.975,col="red")
      abline(v=rasmussen_depths[eventnumber],lty=3)

      lines(x=margt0[,1],y=normt0.y,col="blue",lwd=2)
      lines(x=margt1[,1],y=normt1.y,col="blue",lwd=2,lty=3)
      # ybottom = min(temp_d18O$linramp$data$y)
      # ytop = min(temp_d18O$linramp$linrampfit$q0.025)
      # margt0=temp_d18O$linramp$param$t0$marg.t0
      # normt0.y = margt0[,2]/diff(range(margt0[,2]))*(ytop-ybottom)-min(margt0[,2])+ybottom
      # lines(x=margt0[,1],y=normt0.y,col="blue",lwd=2)
      # ybottom = min(temp_d18O$linramp$data$y)
      # ytop = min(temp_d18O$linramp$linrampfit$q0.025)
      # margt1 = temp_d18O$linramp$param$t1$marginal
      # normt1.y = margt1[,2]/diff(range(margt1[,2]))*(ytop-ybottom)-min(margt1[,2])+ybottom
      # lines(x=margt1[,1],y=normt1.y,col="blue",lwd=2,lty=3)
    }
  }
  temp_dust = linrampfitter(results_dust,control.linramp_dust)
  if(do.plot.rampfit){
    {
      ybottom = min(temp_dust$linramp$data$y)
      ytop = min(temp_dust$linramp$linrampfit$q0.025)
      epsilon = (ytop-ybottom)*0.3

      margt0=temp_dust$linramp$param$t0$marg.t0
      normt0.y = (margt0[,2]-min(margt0[,2]))/diff(range(margt0[,2]))*(ytop-ybottom)+ybottom-epsilon
      margt1 = temp_dust$linramp$param$t1$marginal
      normt1.y = margt1[,2]/diff(range(margt1[,2]))*(ytop-ybottom)-min(margt1[,2])+ybottom-epsilon

      yrange = range(temp_dust$linramp$data$y,temp_dust$linramp$linrampfit$q0.025,
                     temp_dust$linramp$linrampfit$q0.975,
                     normt0.y,normt1.y)

      plot(temp_dust$linramp$data$x,temp_dust$linramp$data$y,type="l",col="gray",
          xlim=rev(range(depth[interval_dust])), xlab="Depth (m)",ylab=expression(paste("log(Ca)","")),
          main=paste0(eventnumber," (logdust): ", event_intervals[eventnumber,2]),
          ylim=yrange)
      lines(temp_d18O$linramp$data$x,temp_dust$linramp$linrampfit$mean)
      lines(temp_d18O$linramp$data$x,temp_dust$linramp$linrampfit$q0.025,col="red")
      lines(temp_d18O$linramp$data$x,temp_dust$linramp$linrampfit$q0.975,col="red")
      abline(v=rasmussen_depths[eventnumber],lty=3)

      lines(x=margt0[,1],y=normt0.y,col="blue",lwd=2)
      lines(x=margt1[,1],y=normt1.y,col="blue",lwd=2,lty=3)

      # plot(temp_dust$linramp$data$x,temp_dust$linramp$data$y,type="l",col="gray",xlim=rev(range(depth[interval_dust])), xlab="Depth (m)",ylab=expression(paste("log(Ca)","")),
      #     main=paste0(eventnumber," (logdust): ", event_intervals[eventnumber,2]))
      # # plot(depth[interval_d18O],logdust[interval_d18O],type="l",col="gray",xlim=rev(range(depth[interval_dust])), xlab="Depth (m)",ylab=expression(paste("log(Ca)","")),
      # #     main=paste0(eventnumber," (logdust): ", event_intervals[eventnumber,2]))
      # lines(temp_dust$linramp$data$x,temp_dust$linramp$linrampfit$mean)
      # lines(temp_dust$linramp$data$x,temp_dust$linramp$linrampfit$q0.025,col="red")
      # lines(temp_dust$linramp$data$x,temp_dust$linramp$linrampfit$q0.975,col="red")
      # abline(v=rasmussen_depths[eventnumber],lty=3)
      # 
      # ybottom = min(temp_dust$linramp$data$y)
      # ytop = min(temp_dust$linramp$linrampfit$q0.025)
      # margt0=temp_dust$linramp$param$t0$marg.t0
      # normt0.y = margt0[,2]/diff(range(margt0[,2]))*(ytop-ybottom)-min(margt0[,2])+ybottom
      # lines(x=margt0[,1],y=normt0.y,col="blue",lwd=2)
      # ybottom = min(temp_dust$linramp$data$y)
      # ytop = min(temp_dust$linramp$linrampfit$q0.025)
      # margt1 = temp_dust$linramp$param$t1$marginal
      # normt1.y = margt1[,2]/diff(range(margt1[,2]))*(ytop-ybottom)-min(margt1[,2])+ybottom
      # lines(x=margt1[,1],y=normt1.y,col="blue",lwd=2,lty=3)
    }
  }
